---
title: "Quiz"
author: "Abdellah Janid"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





# Week 2: 
1) Suppose I define the following function in R
```{r}
cube <- function(x, n) {
        x^3
}
```

```{r}
cube(3)
```

- [X] The number 27 is returned
- [ ] The users is prompted to specify the value of 'n'.
- [ ] An error is returned because 'n' is not specified in the call to 'cube'
- [ ] A warning is given with no value returned.




2) The following code will produce a warning in R.
```{r}
x <- 1:10
if(x > 5) {
        x <- 0
}
```


- [ ] The syntax of this R expression is incorrect.
- [ ] You cannot set 'x' to be 0 because 'x' is a vector and 0 is a scalar.
- [ ] The expression uses curly braces.
- [X] 'x' is a vector of length 10 and 'if' can only test a single logical statement.
- [ ] There are no elements in 'x' that are greater than 5



3) Consider the following function

```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
```

If I then run in R

```{r}
z <- 10
f(3)
```


What value is returned?

- [ ] 4
- [X] 10
- [ ] 16
- [ ] 7



4) Consider the following expression:

```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
```


#################################### From here on I will try to be faster, finish first and note only !!! and ???

5)
```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```

