---
title: "Quiz"
author: "Abdellah Janid"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





# Week 2: Programming with R
1) Suppose I define the following function in R
```{r}
cube <- function(x, n) {
        x^3
}
```

```{r}
cube(3)
```

- [X] The number 27 is returned
- [ ] The users is prompted to specify the value of 'n'.
- [ ] An error is returned because 'n' is not specified in the call to 'cube'
- [ ] A warning is given with no value returned.




2) The following code will produce a warning in R.
```{r}
x <- 1:10
if(x > 5) {
        x <- 0
}
```


- [ ] The syntax of this R expression is incorrect.
- [ ] You cannot set 'x' to be 0 because 'x' is a vector and 0 is a scalar.
- [ ] The expression uses curly braces.
- [X] 'x' is a vector of length 10 and 'if' can only test a single logical statement.
- [ ] There are no elements in 'x' that are greater than 5



3) Consider the following function

```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
```

If I then run in R

```{r}
z <- 10
f(3)
```


What value is returned?

- [ ] 4
- [X] 10
- [ ] 16
- [ ] 7



4) Consider the following expression:

```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
```


#################################### From here on I will try to be faster, finish first and note only !!! and ???

5)
```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```



# Week 3: Loop functions and debugging

1.Question 1
Take a look at the 'iris' dataset that comes with R. The data can be loaded with the code:

```{r}
library(datasets)
data(iris)
?iris
```
```{r}
round(tapply(iris$Sepal.Length, iris$Species, mean))
```

2.Question 2
Continuing with the 'iris' dataset from the previous Question, what R code returns a vector of the means of the variables 'Sepal.Length', 'Sepal.Width', 'Petal.Length', and 'Petal.Width'?

- [ ] rowMeans(iris[, 1:4])
- [X] apply(iris[, 1:4], 2, mean)
- [ ] apply(iris, 2, mean)
- [ ] colMeans(iris)
- [ ] apply(iris, 1, mean)
- [ ] apply(iris[, 1:4], 1, mean)

3.Question 3
Load the 'mtcars' dataset in R with the following code

```{r}
library(datasets)
data(mtcars)
```

There will be an object names 'mtcars' in your workspace. You can find some information about the dataset by running
```{r}
?mtcars
```

How can one calculate the average miles per gallon (mpg) by number of cylinders in the car (cyl)? Select all that apply.

```{r}
tapply(mtcars$mpg, mtcars$cyl, mean)

```



- [ ] `tapply(mtcars$cyl, mtcars$mpg, mean)`
- [ ] `apply(mtcars, 2, mean)`
- [X] `with(mtcars, tapply(mpg, cyl, mean))`
- [ ] `lapply(mtcars, mean)`
- [ ] `mean(mtcars$mpg, mtcars$cyl)`
- [X] `sapply(split(mtcars$mpg, mtcars$cyl), mean)`
- [ ] `split(mtcars, mtcars$cyl)`
- [ ] `sapply(mtcars, cyl, mean)`
- [X] `tapply(mtcars$mpg, mtcars$cyl, mean)`

4.Question 4
Continuing with the 'mtcars' dataset from the previous Question, what is the absolute difference between the average horsepower of 4-cylinder cars and the average horsepower of 8-cylinder cars?

(Please round your final answer to the nearest whole number. Only enter the numeric result and nothing else.)

```{r}
avehr_by_ctl <- tapply(mtcars$hp, mtcars$cyl, mean)
round(abs(avehr_by_ctl["8"]-avehr_by_ctl["4"]))
```


5.Question 5
If you run

```{r}
debug(ls)
```

- [ ] what happens when you next call the 'ls' function?
- [ ] The 'ls' function will execute as usual.
- [ ] Execution of 'ls' will suspend at the beginning of the function and you will be in the browser.
- [ ] The 'ls' function will return an error.
- [ ] You will be prompted to specify at which line of the function you would like to suspend execution and enter the browser.



# Week 4: Programming with R



1.Question 1
What is produced at the end of this snippet of R code?



- [ ] It is impossible to tell because the result is random
- [X] A vector with the numbers 1, 1, 2, 4, 1
- [ ] A vector with the numbers 1, 4, 1, 1, 5
- [ ] A vector with the numbers 3.3, 2.5, 0.5, 1.1, 1.7



```{r}
set.seed(1)
x <- rpois(5, 2)
```

2.Question 2
What R function can be used to generate standard Normal random variables?

- [ ] rnorm
- [ ] pnorm
- [ ] qnorm
- [ ] dnorm

3.Question 3
When simulating data, why is using the set.seed() function important? Select all that apply.

- [ ] It can be used to generate non-uniform random numbers.
- [ ] It ensures that the random numbers generated are within specified boundaries.
- [ ] It ensures that the sequence of random numbers is truly random.
- [X] It ensures that the sequence of random numbers starts in a specific place and is therefore reproducible.


4.Question 4
Which function can be used to evaluate the inverse cumulative distribution function for the Poisson distribution?

- [X] qpois
- [ ] dpois
- [ ] rpois
- [ ] ppois


5.Question 5
What does the following code do?

- [ ] Generate random exponentially distributed data
- [X] Generate data from a Normal linear model
- [ ] Generate data from a Poisson generalized linear model
- [ ] Generate uniformly distributed random data



```{r}
set.seed(10)
x <- rep(0:1, each = 5)
e <- rnorm(10, 0, 20)
y <- 0.5 + 2 * x + e

plot(x,y)
hist(e)
```


6.Question 6
What R function can be used to generate Binomial random variables?

- [ ] pbinom
- [X] rbinom
- [ ] qbinom
- [ ] dbinom

7.Question 7
What aspect of the R runtime does the profiler keep track of when an R expression is evaluated?

- [X] the function call stack
- [ ] the global environment
- [ ] the working directory
- [ ] the package search list




8.Question 8
Consider the following R code

```{r}
library(datasets)
Rprof()
fit <- lm(y ~ x1 + x2)
Rprof(NULL)
```

(Assume that y, x1, and x2 are present in the workspace.) Without running the code, what percentage of the run time is spent in the 'lm' function, based on the 'by.total' method of normalization shown in 'summaryRprof()'?


- [ ] 50%
- [X] 100% #CHECK!!!
- [ ] 23%
- [ ] It is not possible to tell

9.Question 9
When using 'system.time()', what is the user time?

- [X] It is the time spent by the CPU evaluating an expression #CHECK
- [ ] It is the time spent by the CPU waiting for other tasks to finish
- [ ] It is the "wall-clock" time it takes to evaluate an expression
- [ ] It is a measure of network latency


10.Question 10
If a computer has more than one available processor and R is able to take advantage of that, then which of the following is true when using 'system.time()'?

- [ ] user time is 0
- [X] elapsed time may be smaller than user time #CHECKc
- [ ] elapsed time is 0
- [ ] user time is always smaller than elapsed time




