---
title: "Quiz"
author: "Abdellah Janid"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





# Week 2: Programming with R
1) Suppose I define the following function in R
```{r}
cube <- function(x, n) {
        x^3
}
```

```{r}
cube(3)
```

- [X] The number 27 is returned
- [ ] The users is prompted to specify the value of 'n'.
- [ ] An error is returned because 'n' is not specified in the call to 'cube'
- [ ] A warning is given with no value returned.




2) The following code will produce a warning in R.
```{r}
x <- 1:10
if(x > 5) {
        x <- 0
}
```


- [ ] The syntax of this R expression is incorrect.
- [ ] You cannot set 'x' to be 0 because 'x' is a vector and 0 is a scalar.
- [ ] The expression uses curly braces.
- [X] 'x' is a vector of length 10 and 'if' can only test a single logical statement.
- [ ] There are no elements in 'x' that are greater than 5



3) Consider the following function

```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
```

If I then run in R

```{r}
z <- 10
f(3)
```


What value is returned?

- [ ] 4
- [X] 10
- [ ] 16
- [ ] 7



4) Consider the following expression:

```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
```


#################################### From here on I will try to be faster, finish first and note only !!! and ???

5)
```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```



# Week 3: Loop functions and debugging

1.Question 1
Take a look at the 'iris' dataset that comes with R. The data can be loaded with the code:

```{r}
library(datasets)
data(iris)
?iris
```
```{r}
round(tapply(iris$Sepal.Length, iris$Species, mean))
```

2.Question 2
Continuing with the 'iris' dataset from the previous Question, what R code returns a vector of the means of the variables 'Sepal.Length', 'Sepal.Width', 'Petal.Length', and 'Petal.Width'?

- [ ] rowMeans(iris[, 1:4])
- [X] apply(iris[, 1:4], 2, mean)
- [ ] apply(iris, 2, mean)
- [ ] colMeans(iris)
- [ ] apply(iris, 1, mean)
- [ ] apply(iris[, 1:4], 1, mean)

3.Question 3
Load the 'mtcars' dataset in R with the following code

```{r}
library(datasets)
data(mtcars)
```

There will be an object names 'mtcars' in your workspace. You can find some information about the dataset by running
```{r}
?mtcars
```

How can one calculate the average miles per gallon (mpg) by number of cylinders in the car (cyl)? Select all that apply.

```{r}
tapply(mtcars$mpg, mtcars$cyl, mean)

```



- [ ] `tapply(mtcars$cyl, mtcars$mpg, mean)`
- [ ] `apply(mtcars, 2, mean)`
- [X] `with(mtcars, tapply(mpg, cyl, mean))`
- [ ] `lapply(mtcars, mean)`
- [ ] `mean(mtcars$mpg, mtcars$cyl)`
- [X] `sapply(split(mtcars$mpg, mtcars$cyl), mean)`
- [ ] `split(mtcars, mtcars$cyl)`
- [ ] `sapply(mtcars, cyl, mean)`
- [X] `tapply(mtcars$mpg, mtcars$cyl, mean)`

4.Question 4
Continuing with the 'mtcars' dataset from the previous Question, what is the absolute difference between the average horsepower of 4-cylinder cars and the average horsepower of 8-cylinder cars?

(Please round your final answer to the nearest whole number. Only enter the numeric result and nothing else.)

```{r}
avehr_by_ctl <- tapply(mtcars$hp, mtcars$cyl, mean)
round(abs(avehr_by_ctl["8"]-avehr_by_ctl["4"]))
```


5.Question 5
If you run

```{r}
debug(ls)
```

- [ ] what happens when you next call the 'ls' function?
- [ ] The 'ls' function will execute as usual.
- [ ] Execution of 'ls' will suspend at the beginning of the function and you will be in the browser.
- [ ] The 'ls' function will return an error.
- [ ] You will be prompted to specify at which line of the function you would like to suspend execution and enter the browser.


