---
title       : Introduction to the R Language
subtitle    : Loop Functions - apply
author      : Roger Peng, Associate Professor
job         : Johns Hopkins Bloomberg School of Public Health
logo        : bloomberg_shield.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
url:
  lib: ../../libraries
  assets: ../../assets
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## apply

`apply` is used to a evaluate a function (often an anonymous one) over the margins of an array.

- It is most often used to apply a function to the rows or columns of a matrix

- It can be used with general arrays, e.g. taking the average of an array of matrices 

- It is not really faster than writing a loop, but it works in one line!

---

## apply

```{r}
str(apply)
```

- `X` is an array
- `MARGIN` is an integer vector indicating which margins should be “retained”. 
- `FUN` is a function to be applied
- ... is for other arguments to be passed to `FUN`

---

## apply

```{r}
x <- matrix(rnorm(200), 20, 10)
apply(x, 2, mean) #returns the mean of each colums of the matrix x
                  # x; the matrix
                  # 2, means colums
                  # mean; function to apply

apply(x, 1, sum)
x[,1]
```

---

## col/row sums and means

For sums and means of matrix dimensions, we have some shortcuts.

- `rowSums` = `apply(x, 1, sum)`
- `rowMeans` = `apply(x, 1, mean)`
- `colSums` = `apply(x, 2, sum)`
- `colMeans` = `apply(x, 2, mean)`

The shortcut functions are _much_ faster, but you won’t notice unless you’re using a large matrix.

```{r}
colMeans(x[,1:3]) #computes the mean of specified columns
```

---

## Other Ways to Apply

Quantiles of the rows of a matrix.

```{r}
x <- matrix(rnorm(200), 20, 10)
apply(x, 1, quantile, probs = c(0.25, 0.75))
```

---

## apply

Average matrix in an array

```{r}
#Multidimentional array: TODO again
a <- array(rnorm(2 * 2 * 10), c(2, 2, 10))
```

```{r}

apply(a, c(1, 2), mean)

rowMeans(a, dims = 2)
```