---
title: "Week1"
author: "Abdellah Janid"
date: "12/26/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



1.Question 1
The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv

and load the data into R. The code book, describing the variable names is here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf

How many properties are worth $1,000,000 or more?

```{r,dependson="data"}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv"
download.file(fileUrl,destfile="./data/USA_csurvey.csv",method="curl")
USA_csurvey <- read.csv("./data/USA_csurvey.csv")
table(USA_csurvey$VAL)
```


2.Question 2
Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?


Tidy data has no missing values.
Tidy data has one variable per column.
Each variable in a tidy data set has been transformed to be interpretable.
Numeric values in tidy data can not represent categories.


3.Question 3
Download the Excel spreadsheet on Natural Gas Aquisition Program here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called: dat

```{r}
library(xlsx)
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx"
download.file(fileUrl,destfile="./data/dat.xlsx",method="curl")
dat <- read.xlsx("./data/dat.xlsx",sheetIndex=1, rowIndex = 18:23, colIndex = 7:15)

sum(dat$Zip*dat$Ext,na.rm=T)
```


4.Question 4
Read the XML data on Baltimore restaurants from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml

How many restaurants have zipcode 21231?

156
127
100
17

```{r}
library(XML)
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
download.file(fileUrl,destfile="./data/restaurant.xml")
doc <-  xmlTreeParse("./data/restaurant.xml",useInternalNodes=TRUE)
rootNode <- xmlRoot(doc)

zipcodes <- xpathSApply(rootNode,"//zipcode",xmlValue)
table(zipcodes)["21231"]
```


5.Question 5
The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

using the fread() command load the data into an R object

```{r}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
download.file(fileUrl, destfile = "./data/USA_survey_5.csv")

DT <- data.table::fread("./data/USA_survey_5.csv")

system.time(DT[,mean(pwgtp15),by=SEX])
```


