---
title       : Introduction to the R Language
subtitle    : Loop Functions - tapply
author      : Roger Peng, Associate Professor
job         : Johns Hopkins Bloomberg School of Public Health
logo        : bloomberg_shield.png
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
url:
  lib: ../../libraries
  assets: ../../assets
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## tapply

`tapply` is used to apply a function over subsets of a vector. I don’t know why it’s called `tapply`.

```r
> str(tapply)
function (X, INDEX, FUN = NULL, ..., simplify = TRUE)
```

- `X` is a vector
- `INDEX` is a factor or a list of factors (or else they are coerced to factors) 
- `FUN` is a function to be applied
- ... contains other arguments to be passed `FUN`
- `simplify`, should we simplify the result?

---

## tapply

Take group means.

```{r}
x <- c(rnorm(10), runif(10), rnorm(10, 1))
f <- gl(3, 10)
f

tapply(x, f, mean)
mean(x[1:10])
```

---

## tapply

Take group means without simplification.

```r
> tapply(x, f, mean, simplify = FALSE)
$‘1‘
[1] 0.1144464

$‘2‘
[1] 0.5163468

$‘3‘
[1] 1.246368
```

---

## tapply

Find group ranges.

```r
> tapply(x, f, range)
$‘1‘
[1] -1.097309  2.694970

$‘2‘
[1] 0.09479023 0.79107293

$‘3‘
[1] 0.4717443 2.5887025
```

---

## split

`split` takes a vector or other objects and splits it into groups determined by a factor or list of factors.

```r
> str(split)
function (x, f, drop = FALSE, ...)
```

- `x` is a vector (or list) or data frame
- `f` is a factor (or coerced to one) or a list of factors
- `drop` indicates whether empty factors levels should be dropped

---

## split

```r
> x <- c(rnorm(10), runif(10), rnorm(10, 1))
> f <- gl(3, 10)
> split(x, f)
$‘1‘
 [1] -0.8493038 -0.5699717 -0.8385255 -0.8842019
 [5]  0.2849881  0.9383361 -1.0973089  2.6949703
 [9]  1.5976789 -0.1321970
 
$‘2‘
 [1] 0.09479023 0.79107293 0.45857419 0.74849293
 [5] 0.34936491 0.35842084 0.78541705 0.57732081
 [9] 0.46817559 0.53183823
 
$‘3‘
 [1] 0.6795651 0.9293171 1.0318103 0.4717443
 [5] 2.5887025 1.5975774 1.3246333 1.4372701
```

---

## split

A common idiom is `split` followed by an `lapply`.

```r
> lapply(split(x, f), mean)
$‘1‘
[1] 0.1144464

$‘2‘
[1] 0.5163468

$‘3‘
[1] 1.246368
```

---

## Splitting a Data Frame

```{r}
library(datasets)
head(airquality)
```

---

## Splitting a Data Frame

```{r}
s <- split(airquality, airquality$Month)
lapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")]))
```

---

## Splitting a Data Frame

```r
> sapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")])) 
               5         6          7        8        9
Ozone         NA        NA         NA       NA       NA
Solar.R       NA 190.16667 216.483871       NA 167.4333
Wind    11.62258  10.26667   8.941935 8.793548  10.1800

> sapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")],
                                 na.rm = TRUE))
                  5            6             7            8           9 
Ozone      23.61538     29.44444     59.115385    59.961538   31.44828 
Solar.R   181.29630    190.16667    216.483871   171.857143  167.43333 
Wind       11.62258     10.26667      8.941935     8.793548   10.18000
```

---

## Splitting on More than One Level

```{r}
x <- rnorm(10)
f1 <- gl(2, 5)
f2 <- gl(5, 2)
f1
f2
interaction(f1, f2)
```

---

## Splitting on More than One Level

Interactions can create empty levels.

```{r}
str(split(x, list(f1, f2)))
```

---

## split

Empty levels can be dropped.

```r
> str(split(x, list(f1, f2), drop = TRUE))
List of 6
 $ 1.1: num [1:2] -0.378  0.445
 $ 1.2: num [1:2] 1.4066 0.0166
 $ 1.3: num -0.355
 $ 2.3: num 0.315
 $ 2.4: num [1:2] -0.907  0.723
 $ 2.5: num [1:2] 0.732 0.360
```